---
title: "CSW Partner Survey"
author: "Christine Vandenberghe"
date: "31/03/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Online versions of the Community Social Work (CSW) Partner Survey were emailed by Research and Reporting to Partners identified on CSW Spreadsheets on November 29, 2020. A reminder to complete the survey was provided on December 10, with the survey closing December 31. 

## Who Completed the Survey

- One hundred and eleven Partners responded out of a total of 351 Partners listed on CSW Spreadsheets, for a **response rate** of *32%*.
- Fifteen Hub Partners responded out of a total of 98 Hub Partners listed on CSW Spreadsheets, for a **response rate** of *15%*.


```{r}
library(tidyverse)
library(janitor)
```
```{r}
X2020_CSW_Partner_Survey <- read_csv("X2020_CSW_Partner_Survey.csv")
```

```{r}
X2020_CSW_Partner_Survey %>%
  tabyl(Q3,Q5) %>% 
  adorn_percentages(c("row","col")) %>% 
  adorn_pct_formatting(digits=0,rounding = "half up") %>% 
  adorn_ns() %>% 
  adorn_title(placement = "combined")
```

```{r}
X2020_CSW_Partner_Survey %>%
  count(Q9R1) %>% 
  arrange(desc(n))
```

```{r}
X2020_CSW_Partner_Survey %>%
  summarize(mean_time_taken = mean(Time_Taken))
```

```{r}

ggplot(data = X2020_CSW_Partner_Survey,
       mapping = aes(x = Q3,
                     y = Q4,
                     fill=Q4)) +
  geom_bar(stat = "identity")+
  coord_flip()
```